### 2025-01-26 technical_doc/introduction.tex
finish converting some code to diagrams

This document is an example of a software manual created using \LaTeX\ and Overleaf. It provides a nice clean format for producing this type of technical document.

Simply start writing your document and use the Recompile button to view the updated PDF preview. Examples of commonly used commands and features can be found in the sections below, to help you get started.

To change the logo shown on the front page, simply upload your own logo image file (via the file-tree menu) to replace the default logo.pdf file.

Once you're familiar with the editor, you can find various project settings in the Overleaf menu, accessed via the button in the very top left of the editor. To view tutorials, user guides, and further documentation, please visit our \url{https://www.overleaf.com/learn}. If you haven't used \LaTeX\ before, our \url{https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes} tutorial is an excellent place to start.

For large documents, it can be useful to split the document into multiple source files.
Double-clicking on text in Overleaf's PDF preview will take you directly to the corresponding code in the editor.

>>>>

The purpose of this technical document is to provide a comprehensive, interpretable guide for all stakeholders to understand the library. The requirements that were gathered will first be presented. Then there will be an explanation of the architecture and designs that will go towards fulfilling the requirements and constraints. This includes the different modules and their roles in performing operator learning in the Fourier domain using LSSVR\@. The designs will also discuss the way the modules will interface with external stimuli. From the designs, the implementation will be tested on its adherence to restrictions and the designs as a whole.

\section{Scope}
This document will cover the requirements, design and analysis, implementation, and testing of the library. The library is a software product developed with the purpose of providing functionality relevant to our proposed SpectralSVR operator learning approach.

\section{Outline}
This document will be organized as follows:
\begin{enumerate}
    \item Introduction: This chapter provides context to the purpose of this document. This chapter also describes the scope and structure of this document.
    \item Requirements: This chapter explains the software requirements, including functional requirements, non-functional requirements, information requirements, user characteristics, and external interface requirements.
    \item Use Case: This chapter explains the model used based on the results of the software requirements analysis. The model created consists of a rich picture diagram that visualize the use case for the software product.
    \item Design: This chapter explains the software design using Sequence Diagram and module descriptions.
    \item Implementation: This chapter explains the implementation of the software in a specific programming language.
    \item Testing: This chapter contains the process of testing the software using specific test cases. The current results of said test cases are also presented.
\end{enumerate}

### 2025-01-26 technical_doc/requirements.tex
finish converting some code to diagrams

% !TEX root = ./technical_doc.tex
\chapter{REQUIREMENTS}

>>>>

% !TEX root = ./technical_doc.tex
\chapter{REQUIREMENTS}
The requirements of the software can be divided into two main categories of functional and non-functional requirements. The functional requirements of the software are:\nopagebreak
\begin{itemize}
    \item The ability to transform between discrete function values and the coefficients of their Fourier series approximation.
    \item The ability to visualize functions in their coefficient representation
    \item The ability to represent differential equations using Fourier series and the coefficient relation between parameters and solution.
    \item Generation of random functions.
    \item Generate parameters and solutions for the derivative equation and Burgers' equation.
    \item A way to represent complex numbers as a pair of real numbers.
    \item An LSSVR model for regressing the coefficient relationship of parameter and solutions.
    \item A way to normalize inputs to the LSSVR.
    \item A way to measure the accuracy and efficiency of the model.
    \item A way to interpret the coefficient relationship learned by the model.
    \item The ability to use the tools in a Jupyter Notebooks or Python scripts.
\end{itemize}

\noindent The non-functional requirements for the software are:\nopagebreak
\begin{itemize}
    \item Working memory footprint that fits within 16 GB\@.
    \item Efficient and fast performance.
    \item Reliability and the consistency.
    \item Extendable to other problems.
\end{itemize}
\filbreak
\noindent The information requirements of the software are:
\begin{itemize}
    \item Reference of derivative and Burgers' equations.
    \item Mathematical formulation of LSSVR.
    \item Mathematical formulation of the Discrete Fourier Transform (DFT) and properties of the basis and its coefficients.
\end{itemize}

\noindent The external interface requirements are:\nopagebreak
\begin{itemize}
    \item Data compatibility with Zarr or other data formats.
\end{itemize}

### 2025-01-26 technical_doc/usecase.tex
finish converting some code to diagrams

% !TEX root = ./technical_doc.tex
\chapter{USE CASE}

>>>>

% !TEX root = ./technical_doc.tex
\chapter{USE CASE}
The model that will be used based on the requirements is shown in \lccref{fig:rich_picture}. The systems one would like to model using this library may or may not have governing equations that are defined to describe its behavior. In both cases, the measurements of said systems are typically discrete values representing some state of the systems such as temperature distribution. Other measurements may include the thermal conductivity distribution of systems or heat source distribution. Together these form the effect and causes of said system.
\begin{figure}[H]
    \centering
    \includegraphics[width=1.0\linewidth]{figures/rich_picture.png}
    \caption{Rich picture diagram illustrating the environment and use case for the library.}\label{fig:rich_picture}
\end{figure}

Functions from measurements or synthetically generated using known governing equations can be represented as the Fourier coefficients of their approximating Fourier series. As the computation must be able to switch between the physical and Fourier domain, other utilities to change the data format will also be essential. Because the relationship between solutions and the parameters can be learned as the relationship between the coefficients of their parameters, the Least-Squares Support Vector Regression is used to learn this from data. Evaluation of how well the model performs will also be required to understand areas of improvement.
